---
title: "My dynamic report"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library("tidyverse")

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSq8F0qiYCZq4PkAi_R4hqZzWfP71FXaOV9Nhe_H-A5z6WCii-Q9AgSGIW83A6pB2aHbpjy6G_3fi-f/pub?output=csv")
latest_data <- rename(logged_data, timestamp = 1, first_letter = 2, yellow_tiles_count = 3, solved = 4, guess_count = 5, rated_difficulty = 6, last_guess_green_tiles_count = 7)

```

```{css}
body {
  background-color: #36454F;
  color: white;
  font-size: 18px;
  font-family: cursive;
}

pre {
  background-color: #3a3a3a;
  color: white;
  font-size: 18px;
  text-shadow: 0 0 0;
}

h2 {
  color: yellow;
  text-align: center;
  text-shadow: 0 0 3px #fff;
}

h4 {
  color: white;
  text-align: right;
  text-shadow: 0 0 3px #fff;
}

```

## Daily Wordle game performance dynamic report.

This dynamic report tracks my performance of the daily Wordle game, including the first letter used for each game, the amount of guesses and whether I had solved that day's game. This report serves to analyse my overall knowledge of the English vocabulary 

```{r}
difficulty_mean <- mean(latest_data$rated_difficulty)
guess_count_mean <- mean(latest_data$guess_count, na.rm = TRUE)
most_yellow_tiles <- max(latest_data$yellow_tiles_count)
least_yellow_tiles <- min(latest_data$yellow_tiles_count)
num_played <- count(latest_data)$n
num_solved <- sum(latest_data$solved == "Yes")
num_failed <- sum(latest_data$solved == "No")
```

Number of games played: `r num_played`

Number of games solved: `r num_solved`

Number of games failed: `r num_failed`

The mean of my difficulty rating of the Wordle daily  is `r difficulty_mean`

The mean number of guesses per winning game is `r guess_count_mean`

The most amount of yellow tiles I got in a game is `r most_yellow_tiles`

The least amount of yellow tiles I got in a game is `r least_yellow_tiles`

```{r}
ggplot(latest_data) +
  geom_bar(aes(y = first_letter, fill = solved)) +
  labs(title = "Win rate with each starting letter", y = "First Letter", x = "Games played") + scale_x_continuous(breaks = scales::pretty_breaks(n = 10))

```


```{r}
ggplot(latest_data) + geom_bar(aes(y = rated_difficulty)) +
  labs(title = "Difficulty rated per game", y = "Difficulty", x = " Games rated") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 8)) + scale_y_continuous(breaks = scales::pretty_breaks(n = 6))
```